---
title: "Advanced Predictive Analytics Project Dashboard"
author: "Anugya Mishra"
format: 
    dashboard:
      logo: DULogo.png
      scrolling: true
      theme: united
embed-resources: true
---

```{r setup, include=FALSE,warning=FALSE}
#include=FALSE will not include r code in output
#warning=FALSE will remove any warnings from output
#include=FALSE will not include r code in output
#warning=FALSE will remove any warnings from output
library(readr)
library(lmtest)
library(DT) #v0.33 datatable()
library(GGally) #v2.2.1
library(ggcorrplot) #v0.1.4.1
library(MASS) #v7.3-60.2 for Boston data
library(flexdashboard) #v0.6.2
library(plotly) #v4.10.4
library(crosstalk) #v1.2.0
library(knitr) #v1.45 kable(digits=)
library(crosstalk) #v1.2.1 SharedData()
library(tidymodels) #v1.2.0
library(parsnip) #v1.2.1 linear_reg(), set_engine(), set_mode(), fit(), predict()
library(yardstick) #v1.3.1 metrics(), rac_auc(), roc_curve(), metric_set(), conf_matrix()
library(dplyr) #v1.1.4 %>%, select(), select_if(), filter(), mutate(), group_by(), 
    #summarize(), tibble()
library(ggplot2) #v3.5.1 ggplot()
library(broom) #v1.0.6 for tidy(), augment(), glance()
library(rsample) #v1.2.1 initial_split()
library(rpart) #v 4.1.19 Partition package to create trees
library(rpart.plot) #v 3.1.1 creates nicer tree plots
library(vip) #v0.3.2 vip()
  #library(parsnip) #v1.2.1 linear_reg(), set_engine(), set_mode(), fit(), predict()
  #library(yardstick) #v1.3.1 metrics(), rac_auc(), roc_curve(), metric_set(), conf_matrix()
  #library(dplyr) #v1.1.4 %>%, select(), select_if(), filter(), mutate(), group_by(), 
    #summarize(), tibble()
  #library(ggplot2) #v3.5.1 ggplot()
  #library(broom) #v1.0.6 for tidy(), augment(), glance()
  #library(rsample) #v1.2.1 initial_split()
library(performance) #v0.12.0 check_model
library(see) #v0.8.4 for check_model plots from performance
library(patchwork) #v1.2.0 for check_model plots from performance
library(kableExtra) #v1.4.0 kable_styling(font_size = 20)

```

```{r load_data}
#Load the data
df_fuel <- read_csv("Fuel Consumption Ratings.csv") 
colnames(df_fuel)<- c("model_year","make","model","vehicle_class","engine_size","cylinders","transmission","fuel_type",
                      "fuel_consumption_city","fuel_consumption_hwy","fuel_consumption_combined","fuel_consumption_combined2",
                      "CO2_emissions","CO2_rating","smog_rating")
df_fuel<-df_fuel %>% 
  select(-fuel_consumption_combined2,-model,-model_year) #removing model year since we only have one year of data, model has too many categories and fuel_consumption_combined2 is the same information as fuel_consumption_combined but with different unit of measurement


```
```{r data_cleaning}

df_fuel<-df_fuel %>% 
  mutate(fuel_type=ifelse(fuel_type=='Z','premium_gasoline', 
                        ifelse(fuel_type=='D','diesel',
                               ifelse(fuel_type=='E','ethanol',
                                      'regular_gasoline')))) #changing to more understandable name
  
df_fuel<-df_fuel %>%
  mutate(CO2_rating=factor(ifelse(CO2_rating<6,"Low", 
                                      'High')),
         smog_rating=factor(ifelse(smog_rating<6,"Low", #converting to qualitative variable
                                      'High'))) 

df_fuel<-df_fuel %>%
  mutate(transmission = ifelse(transmission== "M5" | transmission == "M6" | transmission =="M7", "M",
                               ifelse(transmission== "A6"| transmission== "A7"| transmission== "A8"| transmission== "A9"| transmission== "A10", "A",
                                      ifelse(transmission== "AM8"| transmission== "AM6"| transmission== "AM7", "AM",
                                             ifelse(transmission== "AV"| transmission== "AV1"| transmission== "AV6"| transmission== "AV7"| transmission== "AV8"| transmission== "AV10","AV","AS")))))


df_fuel<-df_fuel %>%
  mutate(make= ifelse(make=="Ford","Ford",
                      ifelse(make=="Porsche","Porsche",
                             ifelse(make=="Chevrolet","Chevrolet",
                                    ifelse(make=="Toyota","Toyota",
                                           ifelse(make=="BMW","BMW", "Others"))))))

df_fuel<-df_fuel %>%
  mutate(vehicle_class=if_else(vehicle_class %in% c("Station wagon: Mid-size","Station wagon: Small","Special purpose vehicle","Van: Passenger"), "Others",if_else(vehicle_class %in% c("Minivan"), "SUV: Standard",if_else(vehicle_class %in% c("Pickup truck: Small", "Pickup truck: Standard"), "Pickup truck",if_else(vehicle_class %in% c("Sport utility vehicle: Standard", "Sport utility vehicle: Small"), "Sport utility vehicle", vehicle_class))))) 

```

# Introduction
## Row
### Column {width=60%}

::: {.card title="Avanced Predictive Analytics Project"}


**Executive Summary**

This project examines the model-specific fuel consumption ratings for new light-duty vehicles for retail sale and its estimated carbon dioxide emission in Canada in 2022-2023. The goals of this analysis to try to predict the CO2 emissions and well as CO2 Rating and Smog Rating for these vehicles. For this analysis, we first perform some exploratory data analysis(EDA) to understand the distribution of the variables and look for relationships among predictors as well as among predictors and the response variables. 


After the EDA, we perform Regression analysis to predict the CO2 emissions for the vehicles using Linear Regression, Regression Trees, Random Forest and Boosted Trees.  Second, we will perform Classification analysis to predict CO2 rating of these vehicles using Classification trees and Logistic Regression. An additional Logistic regression model was also created to predict Smog Ratings, our second response variable. Finally, we summarize the findings from the analysis in our conclusion. 

The **best regression model to predict CO2 emissions was the regression tree** with a *R-squared of 73%* and the **best classification model was the classification tree** with a *Sensitivity of *86%*. 

We find that the variables that decrease CO2 emissions are:

* Vehicles manufactured by Toyota
* Vehicles with AV(continuous variation) transmission
* Vehicles using ethanol fuel"
* Vehicles using regular gasoline fuel

The variables that increase CO2 emissions are:

* Increase in Engine size of vehicles
* Vehicles manufactured by Ford and Porsche
* Vehicle class such as Mini-comapct, Pickup truck, sport utility, SUV,& Two Seater

**The Problem Description**


This project examines model-specific fuel consumption ratings for new light-duty vehicles for retail sale and its estimated carbon dioxide emission in Canada in 2022-2023. For analysis, I will perform both regression and classification analysis based on CO2 emissions, CO2 Ratings and Smog Ratings. 

The goal for the **regression models is to predict the CO2 emissions** for the new light-duty vehicles using the variables in the data set such as engine size, number of cylinders, vehicle class and make, transmission, fuel type and so on. For this analysis, I will begin with an Exploratory Data Analysis (EDA) to examine the distribution of the variables in the dataset as well as relationships between the variables. Next,I will perform Regression analysis to predict the CO2 emissions and ratings.  Various methods will be used in this analysis, such as  **linear regression, Random Forest regression trees, and Boosted Tree**. 

For the classification analysis, I want to predict perform **if a given light-duty vehicle has a low or high CO2/Smog Rating**. Classification methods such **logistic regression and classification trees.** will be used for this analysis.

Finally, all the models will be summarized and compared to provide a conclusion on the model performance for predicting the variables: CO2 emissions, CO2 Rating and Smog Rating and determine what variables helped in the prediction.  

**The Data**

This dataset has 2756 rows and 12 variables. 

**Data Sources**

2022 fuel consumption ratings. (2022, April 6). Kaggle. https://www.kaggle.com/datasets/rinichristy/2022-fuel-consumption-ratings

Fuel consumption ratings - Open Government Portal. (n.d.). https://open.canada.ca/data/en/dataset/98f1a129-f628-4ce4-b24d-6f16bf24dd64

Fuel consumption ratings - 2022 Fuel Consumption Ratings (2023-08-18) - Open Government Portal. (n.d.). https://open.canada.ca/data/en/dataset/98f1a129-f628-4ce4-b24d-6f16bf24dd64/resource/87fc1b5e-fafc-4d44-ac52-66656fc2a245 
:::

### Column {width=40%}
::: {.card title="Variables"}
**TO PREDICT WITH**

* **make**: Name of the company or brand that manufactured the vehicle
* **vehicle_class**: Vehicle categories based on gross vehicle weight rating (GVWR)
* **engine_size**: Volume of vehicle’s cylinder/engine capacity, measures in liters(L)
* **cylinders**: Number of cylinders the vehicle has
* **transmission**: The type of transmission (A = automatic; AM = automated manual; AS = automatic with selector gear lever; AV = continuous variation)
* **fuel_type**: Type of fuel used in the vehicle 
* **fuel_consumption_city**:  City fuel consumption rating for gasoline mode only, measured in L/100 km 
* **fuel_consumption_hwy**: Highway fuel consumption rating for gasoline mode only,  measured in L/100 km
* **fuel_consumption_combined**: Combined fuel consumption rating for gasoline mode only,  measured in L/100 km


**WE WANT TO PREDICT**

* **CO2_emissions**: The tailpipe emissions of carbon dioxide (in grams per kilometer) for combined city and highway driving
* **CO2_rating**: The tailpipe emissions of carbon dioxide rated  Low (ratings from 1-5) or High(ratings from 6-10 on a scale of from 1(worst) to 10(best))
* **Smog_rating**: The tailpipe emissions of smog-forming pollutants rated Low (ratings from 1-5) or High(ratings from 6-10 on a scale of from 1(worst) to 10(best))

:::

# Data Exploration
## Row
### Column {width=25%}
 
::: {.card title="Data Overview"}
From this data we can see that our variables have a variety of different values based on their types. Firstly, CO2 emissions has a mean of 259.2 g/km with a maximum of 608.0 g/km. Fuel consumption rating for city has a mean of 12.51  L/100 km while fuel consumption rating for highway has a mean of 9.36  L/100 km, resulting in an combined average fuel consumption rating of 11.09  L/100 km. Some variables had a lot of categories so their summaries are provided in the bottom table. 

We also notice that CO2 rating and Smog rating variables are categorical variables with two categories: High (if their rating in 6 or above on a scale of 10) and Low (if rating is below 6).

Low and High CO2 ratings have a noticeable difference in the mean CO2 emissions. For transmission, we observe that AV transmission has a comparatively lower average CO2 emissions compared to other categories. Two seater, pickup truck and SUV standard vehicle class have comparatively higher average CO2 emissions.
:::

### Column {width=45%}

::: {.card title="View the Data Summaries" fill="false"}
Let's look at the range of values for each variable in the given dataset.

```{r}
#View data
summary(df_fuel)
```
:::

### Column {width=30%}

```{r}
#| title: Average CO2 Emissions by CO2 Rating 
#| fill: false
df_fuel %>%
  group_by(CO2_rating) %>%
  summarize(n=n(), mean(CO2_emissions)) %>%
  kable(digits=2)
```

```{r}
#| title: Average CO2 Emissions by Smog Rating 
#| fill: false
df_fuel %>%
  group_by(smog_rating) %>%
  summarize(n=n(), mean(CO2_emissions)) %>%
  kable(digits=2)
```

```{r}
#| title: CO2 Emissions by Fuel Type
#| fill: false
df_fuel %>%
  group_by(fuel_type) %>%
  summarize(n=n(),mean(CO2_emissions)) %>%
  kable(digits=2)
```

```{r}
#| title: CO2 Emissions by Transmission
#| fill: false
df_fuel %>%
  group_by(transmission) %>%
  summarize(n=n(),mean(CO2_emissions)) %>%
  kable(digits=2)
```

```{r}
#| title: CO2 Emissions by Make
#| fill: false
df_fuel %>%
  group_by(make) %>%
  summarize(n=n(),mean(CO2_emissions)) %>%
  kable(digits=2)
```

```{r}
#| title: CO2 Emissions by Vehicle Class
#| fill: false
df_fuel %>%
  group_by(vehicle_class) %>%
  summarize(n=n(),mean(CO2_emissions)) %>%
  kable(digits=2)
```


# Data Visualization 
## Row
### Column {width=40%}

::: {.card title="Response Variables relationships with predictors"}

* We observe that 78% of the light-duty vehicles in our dataset have Low CO2 Rating (rating of 5 or below on a scale from 0 to 10). For Smog Rating, the data is a bit more balanced, with 40.5% of the data having Low Smog Rating and 59.5% having High Smog Rating. 

* Looking at the correlation matrix, we see multicollinearity issue between many of the continuous variables so I removed engine_size, Fuel consumption city, and Fuel consumption Highway for the regression models.

* We see a slight positive skew in the CO2 emissions data, but most of the values are concentrated between 100 g/km to 400 g/km.

* Among the potential predictors for CO2 emissions, the strongest relationships occur with the Fuel Consumption variables.

:::

### Column {width = 60%}

```{r, fig.height =2}
#| title: CO2 Rating
ggplot(df_fuel,aes(x=CO2_rating)) + geom_bar()
```

```{r, fig.height = 2}
#| title:  Smog Rating
ggplot(df_fuel, aes(x=smog_rating)) + geom_bar()
```

```{r, fig.height = 2}
#| title:  CO2 Emissions
ggplot(df_fuel, aes(CO2_emissions)) + geom_histogram(bins=20)
```


## Row {.tabset}

### CO2 Emissions vs CO2 rating and Smog Rating
```{r, fig.height = 3.5}
ggpairs(dplyr::select(df_fuel,CO2_emissions,CO2_rating,smog_rating))+
  theme(axis.text.y=element_text(size=7))
```
### CO2 Emissions vs Transmission and Fuel Type
```{r}
ggpairs(dplyr::select(df_fuel,CO2_emissions,transmission,fuel_type))+
  theme(axis.text.x = element_text(angle = 65, size = 7, hjust = 1))+
  theme(axis.text.y=element_text(size=6))

```

### CO2 Emissions vs Make and Vehicle Class
```{r}
ggpairs(dplyr::select(df_fuel,CO2_emissions,make,vehicle_class))+
  theme(axis.text.x = element_text(angle = 65,size = 7, hjust = 1))+
  theme(axis.text.y=element_text(size=6))

```


### Correlation matrix-CO2 Emissions and Continuous Variables
```{r, fig.height = 3.5}
ggcorrplot(cor(dplyr::select(df_fuel,CO2_emissions,engine_size,cylinders,fuel_consumption_city,fuel_consumption_hwy,fuel_consumption_combined)),lab = TRUE, lab_size = 3)
```

### CO2 rating vs Continuous Variables 
```{r, fig.height = 3.5}
ggpairs(dplyr::select(df_fuel,CO2_rating,fuel_consumption_combined,engine_size,cylinders,fuel_consumption_city,fuel_consumption_hwy))+theme(strip.text.x = element_text(size = 5),
           strip.text.y = element_text(size = 5))
```

### Smog Rating vs Continuous Variables 
```{r, fig.height = 3.5}
ggpairs(dplyr::select(df_fuel,smog_rating,fuel_consumption_combined,engine_size,cylinders,fuel_consumption_city,fuel_consumption_hwy))+theme(strip.text.x = element_text(size = 5),
           strip.text.y = element_text(size = 5))
```

### CO2 emissions vs Fuel Type
```{r, fig.height = 3.5}
df_fuel %>% group_by(fuel_type, CO2_rating) %>%
  summarize(n=n()) %>%
  ggplot(aes(y=n, x=CO2_rating,fill=fuel_type)) +
      geom_bar(position="dodge", stat="identity") +
      geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
      ggtitle("CO2 emissions vs Fuel Type") +
      coord_flip() #makes horizontal
```

### CO2 emissions vs Transmission
```{r, fig.height = 3.5}

df_fuel %>% group_by(transmission, CO2_rating) %>%
  summarize(n=n()) %>%
  ggplot(aes(y=n, x=CO2_rating,fill=transmission)) +
      geom_bar(position="dodge", stat="identity") +
      geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
      ggtitle("CO2 emissions vs Transmission") +
      coord_flip() #makes horizontal
```

### CO2 emissions vs Make
```{r, fig.height = 3.5}
### CO2 emissions vs Categorical Variables
df_fuel %>% group_by(make, CO2_rating) %>%
  summarize(n=n()) %>%
  ggplot(aes(y=n, x=CO2_rating,fill=make)) +
      geom_bar(position="dodge", stat="identity") +
      geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
      ggtitle("CO2 emissions vs Make") +
      coord_flip() #makes horizontal
```


# Regression  Models
## Row { .tabset}

### Linear Regression Model Predicting Continuous CO2 Emissions (CO2_emissions)

::: {.card title="Regression Summary"}

To prediction of the continuous variable CO2 Emissions(CO2_emissions), 
first I will use a linear regression model. The results of the model are summarized below.

The full linear regression model had many non-important predictors so we ran a pruned model by only keeping those predictors that are improtant in predicting CO2 emission. However, we observed that reducing the predictors that did not help with prediction of the 
CO2 emission and we saw that the metrics/fit statistics remained very similar to the full model (R-square and RMSE (root mean squared error)).

Looking at the assumption check and residual plots, we observed some issues with our data. We also can see that the the Residuals vs
Fitted curves has patterns. We also failed most of the assumption checks for the linear regression model.
Therefore, this indicates that either we can transform the data for linear regression or predict CO2 emission using some additional models
so see if we can improve the model fit.



**Effect on CO2 emissions by the Predictor Variables**
```{r, cache=TRUE}
#create table summary of predictor changes
predchang = tibble(
  Variable = c(
'engine_size','make_Ford','make_Porsche','make_Toyota','vehicle_class_Minicompact','vehicle_class_Others','vehicle_class_Pickup.truck','vehicle_class_Sport.utility.vehicle','vehicle_class_SUV..Small','vehicle_class_SUV..Standard','vehicle_class_Two.seater','transmission_AV', 'fuel_type_ethanol',
'fuel_type_regular_gasoline' ),
  Direction = c('Increase','Increase','Increase','Decrease','Increase','Increase','Increase','Increase','Increase','Increase','Increase','Decrease','Decrease','Decrease')
)
predchang %>%
  kable(align = 'l') #pretty table output
```

:::

### Linear Regression Full

```{r, cache=TRUE}
#Model and capture metrics
reg_recipe <- recipe(CO2_emissions ~ ., data = dplyr::select(df_fuel,-fuel_consumption_city,-fuel_consumption_hwy,-CO2_rating,-smog_rating)) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_normalize(all_predictors()) %>%
  prep()
df_fuel_reg_norm <- bake(reg_recipe, df_fuel)

#Creating training and testing for regression
set.seed(12934)

CO2_emissions_reg_split <- initial_split(df_fuel_reg_norm,
                            prop = .7) 
df_fuel_reg_norm_train<- rsample::training(CO2_emissions_reg_split)
df_fuel_reg_norm_test<- rsample::testing(CO2_emissions_reg_split)

 #Creates the 5 sets of data

#Define the model specification
reg_spec <- linear_reg() %>% ## Class of problem  
   set_engine("lm") %>% ## The particular function that we use  
   set_mode("regression") ## type of model

#Fit the model
reg1_fit <- reg_spec %>%  
   fit(CO2_emissions ~ .-cylinders-fuel_consumption_combined,data = df_fuel_reg_norm_train)

#Capture the predictions 
pred_reg1_fit <- augment(reg1_fit,df_fuel_reg_norm_test)


#Capture the metrics

curr_metrics <- pred_reg1_fit %>%
  metrics(truth=CO2_emissions,estimate=.pred)

results_reg <- tibble(model = "Linear Model",
                  RMSE = curr_metrics[[1,3]],
                  MAE = curr_metrics[[3,3]],
                  RSQ = curr_metrics[[2,3]]) 
```

::: {.card title="Analysis Summary"}

We can see an R-squared of 79.4% and the residuals mostly pass the normality check but 
for linearity, we see that they skewed at the very end, so there are more values that are more than 0.
Examining the full model, we observe that there are some predictors that are not significant 
in predicting the CO2 emissions, so we will created a pruned version of the model by removing 
non-significant/non-important predictors.

```{r, cache=TRUE}
#Metrics
results_reg %>%
  kable(digits = 2) 
#Residual Histogram
reg1_fit %>%
  check_model(check=c('normality','linearity'))

```

:::

```{r}
#| title: The Full Regression Model Coefficients
tidy(reg1_fit) %>%
  kable(digits=2) 
```

### Linear Regression Final 

```{r}
#Model and capture metrics
reg2_fit <- reg_spec %>%
  fit(CO2_emissions ~ .-cylinders-fuel_consumption_combined-fuel_type_premium_gasoline-transmission_AM-transmission_AS-transmission_M-vehicle_class_Subcompact-vehicle_class_Mid.size-vehicle_class_Full.size-make_Others-make_Chevrolet,data = df_fuel_reg_norm_train)
#Capture the predictions and metrics
pred_reg2_fit <- augment(reg2_fit,df_fuel_reg_norm_test)


curr_metrics <- pred_reg2_fit %>%
  metrics(truth=CO2_emissions,estimate=.pred)

results_new <- tibble(model = "Linear Final Model",
                  RMSE = curr_metrics[[1,3]],
                  MAE = curr_metrics[[3,3]],
                  RSQ = curr_metrics[[2,3]])
results_reg <- bind_rows(results_reg, results_new)
reg2_mae <- curr_metrics %>%
  filter(.metric=='mae') %>%
  pull(.estimate)

```

::: {.card title="Analysis Summary"}

For this analysis we will use a pruned Linear Regression Model.Although the model's R-squared slightly decreased, the difference is less than 0.5% and the model only consists of significant predictors after removing some of the vehicle class, make, fuel type and transmission type categories that were insignificant.

```{r}
#Metrics
results_reg %>%
  kable(digits=3)
```

## Assumption 1 Check: Little to no multi-collinearity

The Variance Inflation Factor (VIF) allows us to check for collinearity amongst the X variables. A general rule is if VIF associated with a variable is > 5 or 10 then - this means we have multicollinearity. We would expect the interaction term to be highly related to the other variables. None of the values fall above 5 so we won't remove any more variables at this point.

```{r assumption_1, fig.height=5}
reg2_fit %>%
  check_model(check='vif')
```
## For linearity, it did not pass the assumption check but the residuals are mostly normally distributed since the residuals distribution follows the distribution of the normal curve.
```{r}
#Assumptions Linearity and Normality 
reg2_fit %>%
  check_model(check=c('normality','homogeneity'))
```
## Assumption 3 Check: Homoscedasticity of errors-contd

The bptest() from the lmtest package can also test for non-constant variances in the residuals. This test is often called the Breusch-Pagan test. The test has a null hypothesis of constant error variance against the alternative that the error variance changes with the level of the response (fitted values), or with a linear combination of predictors.  

When we conducted the bptest, the p-value was small which means that we rejected the null and concluded that the error variance changes/is non-constant. We did not pass this assumption check which is something to keep in mind during prediction.

```{r}
bptest(reg2_fit$fit, data=df_fuel_reg_norm_test, 
       varformula = ~ fitted.values(reg2_fit$fit),
       studentize = TRUE)
```
## Assumption 4 Check: Independence of the observations

Here we can check the independence of the observations with a Durbin Watson test statistic. The Durbin Watson test computes the residual first order autocorrelation. In general values, between 1.5 to 2.5 are relatively normal and we don't worry about them. Since the statistic is very close to 2, we don't see a violation of independence (or evidence of autocorrelation).

```{r assumption_4}
#Assumption 4 Check: Independence of the observations

set.seed(123)
dwtest(reg2_fit$fit, iterations=15)
```
:::

```{r}
#| title: The Final Regression Model Coefficients
tidy(reg2_fit) %>%
  kable(digits=2)
```

```{r, cache=TRUE}
#| title: Compare actual (CO2_emissions) vs predicted (y_hat) for pruned regression model
#| 
#Plot the Actual Versus Predicted Values
ggplotly(ggplot(data = pred_reg2_fit,
            aes(x = .pred, y = CO2_emissions)) +
          geom_point(col = "#6e0000") +
            geom_abline(slope = 1) +
            ggtitle(paste("Pruned Regression with MAE",round(reg2_mae,2))))
```
```{r assumption_3,fig.height=7 }

pred_reg2_fit %>%
  ggplot(aes(y=.resid, x=.pred)) +
    geom_point(col="#6E0000") + 
  geom_hline(yintercept=0, linetype = 3) + 
  geom_hline(yintercept=3, linetype = 2) +
  geom_hline(yintercept=2, linetype = 3) + 
  geom_hline(yintercept=-2, linetype = 3) + 
  geom_hline(yintercept=-3, linetype = 2) +
    scale_x_continuous("Fitted Values") +
    scale_y_continuous("Residuals")

```

## Row { .tabset}

### Regression Trees predicting Vehicle's CO2_emissions (CO2 emissions )


```{r}
#Model and capture metrics
#Define the model specification
tree_reg_spec <- decision_tree() %>%
  set_engine("rpart") %>%
  set_mode("regression")

#Fit the model
tree1_fit <- tree_reg_spec %>%  
   fit(CO2_emissions ~ .,data = df_fuel_reg_norm_train)

#Capture the predictions and metrics
pred_tree1_fit <- augment(tree1_fit,df_fuel_reg_norm_test)

curr_metrics <- pred_tree1_fit %>%
  metrics(truth=CO2_emissions,estimate=.pred)
results_new <- tibble(model = "Reg Tree Model",
                  RMSE = curr_metrics[[1,3]],
                  MAE = curr_metrics[[3,3]],
                  RSQ = curr_metrics[[2,3]])
tree1_mae <- curr_metrics %>%
  filter(.metric=='mae') %>%
  pull(.estimate)
results_reg <- bind_rows(results_reg, results_new)

```

::: {.card title="Regression Tree Summary"}

After examining the Regression Tree, tuned Random Forest trees as well as the tuned boosted tree, we can see that the most important variables for the Regression, RF and Boosted tree are **fuel_consumption_combined (fuel consumption combined for city + highway)** and **engine_size**.  RF and Boosted trees had a better fit compared to the regression tree. The next most important variables for RF and Boosted trees are **cylinders**, and **transmission_AV**. We can see that 

* if there are **higher combined fuel consumption for city and highway**, the **CO2_emissions for the vehicle tends to be higher**.  
* The Boosted tree is suggested since it performs the best out of all the regression trees.
:::

### Regression Tree

::: {.card title="Analysis Summary"}

We will predict the Median Value with all the variables.

```{r}
#Metrics
results_reg %>%
  kable(digits=2)
```

:::

::: {.card title="View the Regression Tree and Variable Importance"}
We see that the regression tree has 9 leaf nodes.
```{r}
#Tree Output
rpart.plot(tree1_fit$fit, roundint=FALSE)
#VI Plot
vip(tree1_fit)
```

:::

::: {.card title="Compare actual (CO2_emissions) vs predicted (y_hat)"}

```{r}
#Plot the Actual Versus Predicted Values
ggplotly(ggplot(data = pred_tree1_fit,
            aes(x = .pred, y = CO2_emissions)) +
  geom_point(col = "#6e0000") +
  geom_abline(slope = 1) +
  ggtitle(paste("Regression Tree with MAE",round(tree1_mae,2))))
```
:::


```{r}
#Define the CV folds and grid parameters
#Creating CV folds
set.seed(4425)

df_fuel_reg_norm_train_folds <- vfold_cv(df_fuel_reg_norm_train, v = 5)

rf_fuel_grid <- expand_grid(mtry = 5:15,
                       trees = c(500, 1000, 1500))


#Define the Model Specification
rf_fuel_tune_spec <- rand_forest(mtry = tune(), 
                            trees = tune()) %>%
                  set_engine("ranger", 
                             importance = "impurity") %>% 
                  set_mode("regression") 

#Define our workflow
fuel_rf_tree_wf <- workflow() %>%
                  add_model(rf_fuel_tune_spec) %>%
                  add_formula(CO2_emissions ~ .)

#Tune on the grid of values
fuel_rf_tree_rs <- fuel_rf_tree_wf %>% 
                    tune_grid(resamples = df_fuel_reg_norm_train_folds,
                              grid = rf_fuel_grid)

#Selecting best parameters for model
final_fuel_rf_tree_wf <- fuel_rf_tree_wf %>% 
                      finalize_workflow(select_best(fuel_rf_tree_rs))

```

```{r}
final_fuel_rf <- final_fuel_rf_tree_wf %>%
                      fit(data = df_fuel_reg_norm_train) 

```


```{r}
pred_final_fuel_rf <- final_fuel_rf %>% 
                          augment(df_fuel_reg_norm_test) 

```




```{r}
#Capture the predictions and metrics

curr_metrics <- pred_final_fuel_rf %>%
  metrics(truth=CO2_emissions,estimate=.pred)

results_new <- tibble(model = "Tuned RF Tree Model",
                  RMSE = curr_metrics[[1,3]],
                  MAE = curr_metrics[[3,3]],
                  RSQ = curr_metrics[[2,3]])

rf_tree_mae <- curr_metrics %>%
  filter(.metric=='mae') %>%
  pull(.estimate)

results_reg <- bind_rows(results_reg, results_new)

```



### Regression Tuned Random Forest Tree

::: {.card title="Analysis Summary"}

We will predict the CO2 emissions of vehicles using all the variables in the Random Forest Model.

* Mtry of 15 and 1500 trees were selected as parameters for the model.

```{r}
#Metrics
results_reg %>%
  kable(digits=3)

final_fuel_rf_tree_wf
```

:::

::: {.card title="View the Variable Importance"}

Fuel consumption combined and engine size are the most important predictors in our RF model.

```{r}

#VIP Plot
final_fuel_rf %>% 
  extract_fit_parsnip() %>% 
  vip(aesthetics = list(fill = "#6e0000", col = "black"))
```

:::

::: {.card title="Compare actual (CO2_emissions) vs predicted (y_hat)"}

```{r}
#Plot the Actual Versus Predicted Values
ggplotly(ggplot(data = pred_final_fuel_rf,
            aes(x = .pred, y = CO2_emissions)) +
  geom_point(col = "#6e0000") +
  geom_abline(slope = 1) +
  ggtitle(paste("Regression Tree with MAE",round(rf_tree_mae,2))))
```
:::


### Tuned Gradient Boosted Tree

```{r}
#Define the Model Specification
xgb_tune_spec <- boost_tree(trees = 500,
                            min_n = 5,
                            #randomness
                            mtry=tune(),
                            #model complexity
                            tree_depth = tune(),
                            loss_reduction = tune(),
                            #step size
                            learn_rate = tune()) %>%
                set_engine("xgboost") %>% 
                set_mode("regression")

#Define the grid parameters

set.seed(23456)


xgb_grid <- grid_latin_hypercube(
              tree_depth(),
              loss_reduction(),
              finalize(mtry(), df_fuel_reg_norm_train),
              learn_rate(),
              size = 10)

#Define workflow
xgb_tune_wf <- workflow() %>%
            add_model(xgb_tune_spec) %>%
            add_formula(CO2_emissions ~ .)

#Tune on the grid of values

boost_rs <- xgb_tune_wf %>% 
              tune_grid(resamples = df_fuel_reg_norm_train_folds,
                        grid = xgb_grid)

#Selecting best parameters
final_boost_tune_wf <- xgb_tune_wf %>% 
                finalize_workflow(select_best(boost_rs))

final_fuel_xgb <- final_boost_tune_wf %>%
                      fit(data = df_fuel_reg_norm_train) 

```


```{r}
#Capture the predictions and metrics
pred_final_fuel_xgb <- final_fuel_xgb %>% 
                            augment(df_fuel_reg_norm_test)

curr_metrics <- pred_final_fuel_xgb %>%
  metrics(truth=CO2_emissions,estimate=.pred)
results_new <- tibble(model = "Tuned Gradient Boosted Tree Model",
                  RMSE = curr_metrics[[1,3]],
                  MAE = curr_metrics[[3,3]],
                  RSQ = curr_metrics[[2,3]])
tree2_mae = curr_metrics %>%
  filter(.metric=='mae') %>%
  pull(.estimate)
results_reg <- bind_rows(results_reg, results_new)

```


::: {.card title="Analysis Summary"}

Let's look at a boosted tree to see if our metrics/results improve.

* The parameters chosen for the boosted model are  mtry = 12, trees = 500, min_n = 5, tree_depth = 9,learn_rate = 0.0328 and loss_reduction = 0.240.

```{r}
results_reg %>%
  kable(digits=3)


final_boost_tune_wf
```

:::

::: {.card title="View the Variable Importance"}

Fuel consumption combined and engine size are the most important predictors in the model.
```{r}

#VIP Plot
final_fuel_xgb %>% 
  extract_fit_parsnip() %>% 
  vip(aesthetics = list(fill = "#6e0000", col = "black"))
```

:::

::: {.card title="Compare actual (CO2_emissions) vs predicted (y_hat) tuned tree"}
```{r}
ggplotly(ggplot(data = pred_final_fuel_xgb,
            aes(x = .pred, y = CO2_emissions)) +
        geom_point(col = "#6e0000") +
        geom_abline(slope = 1) +
        ggtitle(paste("Regression Tuned Gradient Boosted Tree with MAE",round(tree2_mae,2))))
```

:::



# Classification Analysis
## Row { .tabset}
### Tuned Classification Trees Summary

::: {.card title="Classification Models"}

We are using the classification models to predict the high/low CO2 Rating.For the logistic regression, we also predicted the high/low Smog rating. These were coded to categorical in the earlier steps where High means a rating of 6 and above, while low is otherwise.

For this analysis, we will perform a logistic regression and then the classification tree. 

* We observed that the sensitivity of original models for CO2_rating classification were around 99.4%.This means that out of all the vehicles that were actually High rating, 99.4% of them were correctly predicted as High by the model.

* We saw an accuracy of 98.9% for the best model. This means that ratings 98.9% of the observations were correctly predicted as their actual rating(both High and Low).

* Using the best cutoffs for the models, the sensitivity increased to 100%.

* The model I would choose for the classification is because it is easy to explain. The parameters for the classification tree was const complexity of 0.1 and tree depth of 4.

:::

```{r}
#Model and capture metrics
class_CO2_recipe<- recipe(CO2_rating ~ ., data = dplyr::select(df_fuel,-CO2_emissions,-fuel_consumption_city,-fuel_consumption_hwy)) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_normalize(all_numeric()) %>%
  prep()

class_smog_recipe<- recipe(smog_rating ~ ., data = dplyr::select(df_fuel,-CO2_emissions,-fuel_consumption_city,-fuel_consumption_hwy)) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_normalize(all_numeric()) %>%
  prep()
  
df_class_CO2_norm <- bake(class_CO2_recipe, df_fuel)

df_class_smog_norm <- bake(class_smog_recipe, df_fuel)

#Creating training and testing for classification-CO2 rating
set.seed(12934)

CO2_class_split <- initial_split(df_class_CO2_norm,
                            prop = .7,
                            strata = CO2_rating) 

df_CO2_norm_train<- rsample::training(CO2_class_split)
df_CO2_norm_test<- rsample::testing(CO2_class_split)


#Creating training and testing for classification-Smog rating
set.seed(12934)

smog_class_split <- initial_split(df_class_smog_norm,
                            prop = .7,
                            strata = smog_rating) 

df_smog_norm_train<- rsample::training(smog_class_split)
df_smog_norm_test<- rsample::testing(smog_class_split)
```

```{r}
#CO2 rating classification reg model

#Define metric set
my_class_metrics <- metric_set(yardstick::accuracy, yardstick::sensitivity,
                               yardstick::specificity, yardstick::precision)

#Define Model Specifications
CO2_class_tree_tune_spec <- decision_tree(cost_complexity = tune(),
                             tree_depth = tune()) %>% 
                  set_engine("rpart") %>% 
                  set_mode("classification")

set.seed(23432)
#Define the CV folds and grid parameters
fuel_CO2_folds <- vfold_cv(df_CO2_norm_train,v=5)
fuel_CO2_grid <- dials::grid_regular(cost_complexity(),
                                tree_depth(range = c(4, 8)),
                                levels = 5)


#Define our workflow with add_model() and add_formula()
tree_CO2_class_wf <- workflow() %>%
                  add_model(CO2_class_tree_tune_spec) %>%
                  add_formula(CO2_rating ~ .)


#Tune on the grid of values with tune_grid()

tree_CO2_class_rs <- tree_CO2_class_wf %>% 
                 tune_grid(resamples = fuel_CO2_folds,
                          grid = fuel_CO2_grid,
                          metrics=my_class_metrics)


final_CO2_class_tree_wf <- tree_CO2_class_wf %>% 
                        finalize_workflow(select_best(tree_CO2_class_rs, metric='sensitivity'))


final_CO2_class_tree_fit <- final_CO2_class_tree_wf %>%
                        fit(df_CO2_norm_train) %>%
                        extract_fit_parsnip() 


```

```{r}


#Capture the predictions and metrics
pred_class_CO2_tree <- augment(final_CO2_class_tree_fit,df_CO2_norm_test)


curr_metrics <- pred_class_CO2_tree %>%
  my_class_metrics(truth=CO2_rating,estimate=.pred_class)
results_cls <- tibble(model = "Classification Tree CO2 rating Model",
                  Accuracy = curr_metrics[[1,3]],
                  Sensitivity = curr_metrics[[2,3]],
                  Specificity = curr_metrics[[3,3]],
                  Avg_Sens_Spec = (Sensitivity + Specificity)/2,
                  Precision = curr_metrics[[4,3]])
class_tree1_sens <- curr_metrics %>%
  filter(.metric=='sens') %>%
  pull(.estimate)




```

::: {.card title="Classification Tree Summary"}

We will use all the variables except CO2_emissions which is median value because
this is what the medvHigh is created from. For this model we will set
the cost complexity to .001.

```{r}

#Confusion Matrix
pred_class_CO2_tree %>%
  conf_mat(truth=CO2_rating,estimate=.pred_class)

#Metrics
results_cls %>%
  kable(digits = 3, align = 'l')

final_CO2_class_tree_wf
```

:::

::: {.card title="View the Classification Tree and Variable Importance"}

We can see we have 2 leaf nodes. The higher the vip value, the more important the predictor is for classification.
```{r}
#Tree Output
rpart.plot(final_CO2_class_tree_fit$fit, type=1, extra = 102, roundint=FALSE)
#VI Plot
vip(final_CO2_class_tree_fit)
```
:::

### Checking the Classification Tree Cutoff

::: {.card title="View the ROC Curve"}

```{r}
#Plot the ROC curve
#DO NOT EDIT FUNCTION
ROC_graph <- function(pred_data, truth, probs, model_desc="", df_roc = ""){
    #This function creates a ROC Curve. It will return a df_roc with values
    #it used to create the graph. It will also add to a previous ROC curve
    #The inputs are the prediction table (from augment()) and the columns for the
    #truth and probability values. There is also an optional model description
    #and a previous df_roc dataframe. The columns need to be strings (i.e., 'sales')
    #Capture the auc value
    curr_auc <- pred_data %>%
                     roc_auc(truth = {{truth}}, {{probs}}) %>%
                     pull(.estimate)
    #Capture the thresholds and sens/spec
    ###First choice creates a new df_roc table
    if (mode(df_roc) == "character") { #if it is a tibble will be "list"
        df_roc <- pred_data %>% roc_curve(truth = {{truth}}, {{probs}}) %>% 
                          mutate(model = paste(model_desc,round(curr_auc,2)))
    }
    ###Second choice is if there is already a df_roc that was input
    else {
    df_roc <- bind_rows(df_roc,  #use if df_roc exists with other models
                   pred_data %>% roc_curve(truth = {{truth}}, {{probs}}) %>% 
                      mutate(model = paste(model_desc,round(curr_auc,2))))
    }
    #Plot the ROC Curve(s) 
    print(ggplot(df_roc, 
            aes(x = 1 - specificity, y = sensitivity, 
                group = model, col = model)) +
            geom_path() +
            geom_abline(lty = 3)  +
            scale_color_brewer(palette = "Dark2") +
            theme(legend.position = "top") )
    #Capture the roc values in a df to add additional ROC curves
    return(df_roc)
}
#Sample Call
df_roc_CO2_rating <- ROC_graph(pred_class_CO2_tree,"CO2_rating",".pred_High","CO2 Classification tree")
```

:::

::: {.card title="Best Threshold "}

```{r}
#Find Best Threshold cutoff
ROC_threshold <- function(pred_data,truth,probs) {
  #This function finds the cutoff with the max sum of sensitivity and specificity
  #Created tidy version of:
  #http://scipp.ucsc.edu/~pablo/pulsarness/Step_02_ROC_and_Table_function.html
  #The inputs are the prediction table (from augment()) and the columns for the
  #truth and estimate values. The columns need to be strings (i.e., 'sales')

  roc_curve_tbl <- pred_data %>%
                    roc_curve(truth = {{truth}}, {{probs}})
  auc = pred_data %>%
              roc_auc(truth = {{truth}}, {{probs}}) %>%
              pull(.estimate)
  best_row = which.max(roc_curve_tbl$specificity + roc_curve_tbl$sensitivity)
  return(tibble(Best_Cutoff = round(pull(roc_curve_tbl[best_row,'.threshold']),4),
         Sensitivity = round(pull(roc_curve_tbl[best_row,'sensitivity']),4),
         Specificity =round(pull(roc_curve_tbl[best_row,'specificity']),4),
         AUC_for_Model = round(auc,4)))
}


best_cut_ct <- ROC_threshold(pred_class_CO2_tree,'CO2_rating', '.pred_High')
best_cut_ct %>%
  kable(digits=2)
```

```{r}

#Adding a new cutoff prediction column
pred_class_tree2 <- pred_class_CO2_tree %>%
                    mutate(pred_High_bestcut = factor(ifelse(.pred_High > best_cut_ct[[1]],"High","Low"),
                                              levels=c("High","Low")))

# Confusion matrix for Classification Cutoff modified
pred_class_tree2 %>%
  conf_mat(truth=CO2_rating,estimate=pred_High_bestcut)

# Metrics
curr_metrics <- pred_class_tree2 %>%
  my_class_metrics(truth=CO2_rating,estimate=pred_High_bestcut)
results_new <- tibble(model = paste("Classification Tree Model Best Cutoff",round(best_cut_ct[[1]],2)),
                  Accuracy = curr_metrics[[1,3]],
                  Sensitivity = curr_metrics[[2,3]],
                  Specificity = curr_metrics[[3,3]],
                  Avg_Sens_Spec = (Sensitivity + Specificity)/2,
                  Precision = curr_metrics[[4,3]])
results_cls <- bind_rows(results_cls, results_new)
results_cls %>%
  kable(digits=3, align = 'l')
```

:::


## Row { .tabset}

### Logistic Regression-CO2 Rating

::: {.card title="Logistic Summary- CO2 Rating"}


For our final model, we will use logistic regression to explore two response variables- CO2_Rating and Smog Rating.

We observed that fuel consumption combined (city + highway) and Vehicle Class SUV: Small are most important in the model along with the full logistic regression equation.

```{r}
#Model and capture metrics
#Define the model specification
logistic_spec <- logistic_reg() %>%
             set_engine('glm') %>%
             set_mode('classification')

#Fit the model
log_CO2_fit1 <- logistic_spec %>%
              fit(CO2_rating ~ .-cylinders-smog_rating_Low, data = df_CO2_norm_train)

#Capture the predictions and metrics

pred_log_fit1 <- augment(log_CO2_fit1, df_CO2_norm_test)


```

```{r}
tidy(log_CO2_fit1$fit) %>%
  kable(digits=2)
```

:::

::: {.card title="Pruned Logistic Regression Equation"}
```{r}
#Fit the pruned model and capture new metrics
log_CO2_fit2 <- logistic_spec %>%
              fit(CO2_rating ~ fuel_consumption_combined + 	+transmission_AS+vehicle_class_SUV..Small , data = df_CO2_norm_train)


#Capture the predictions and metrics
pred_log_CO2_final_fit <- augment(log_CO2_fit2,df_CO2_norm_test)

curr_metrics <- pred_log_CO2_final_fit %>%
  my_class_metrics(truth=CO2_rating,estimate=.pred_class)
results_new <- tibble(model = "Pruned CO2 Rating Logistic Model",
                  Accuracy = curr_metrics[[1,3]],
                  Sensitivity = curr_metrics[[2,3]],
                  Specificity = curr_metrics[[3,3]],
                  Avg_Sens_Spec = (Sensitivity + Specificity)/2,
                  Precision = curr_metrics[[4,3]])
results_cls <- bind_rows(results_cls, results_new)
class_tree1_sens <- curr_metrics %>%
  filter(.metric=='sens') %>%
  pull(.estimate)
```

```{r}
#Logistic Equation
tidy(log_CO2_fit2$fit) %>%
  kable(digits=2)
```

:::

::: {.card title="Metrics, and VIP Plot"}
```{r}
#Metrics
results_cls %>%
  kable(digits = 2, align = 'l')

#Confusion Matrix
pred_log_CO2_final_fit %>%
  conf_mat(truth=CO2_rating,estimate=.pred_class)


#VIP Plot
vip(log_CO2_fit2)
```

:::

### Checking the Logistic Cutoff
::: {.card title="View the ROC Curve"}

```{r}
#ROC Curve
df_roc_CO2_rating <- ROC_graph(pred_log_CO2_final_fit,"CO2_rating",".pred_High","log", df_roc_CO2_rating)
```

:::

::: {.card title="Best Threshold "}

```{r}
best_cut_log <- ROC_threshold(pred_log_CO2_final_fit,"CO2_rating",".pred_High")
best_cut_log  %>%
  kable(digits=2)

#Adding a new cutoff prediction column
pred_log2_fit <- pred_log_CO2_final_fit %>%
                    mutate(pred_High_bestcut = factor(ifelse(.pred_High > best_cut_log[[1]],"High","Low"),
                                              levels=c("High","Low")))
                                              
# Confusion matrix for Logistic Cutoff 25%
pred_log2_fit %>%
  conf_mat(truth=CO2_rating,estimate=pred_High_bestcut)

# Metrics
curr_metrics <- pred_log2_fit %>%
  my_class_metrics(truth=CO2_rating,estimate=pred_High_bestcut)
results_new <- tibble(model = paste("Logistic Model Best Cutoff",round(best_cut_log[[1]],2)),
                  Accuracy = curr_metrics[[1,3]],
                  Sensitivity = curr_metrics[[2,3]],
                  Specificity = curr_metrics[[3,3]],
                  Avg_Sens_Spec = (Sensitivity + Specificity)/2,
                  Precision = curr_metrics[[4,3]])
results_cls <- bind_rows(results_cls, results_new)
results_cls %>%
  kable(digits = 4, align = 'l')
```
:::

## Row { .tabset}

### Logistic Regression-Smog Rating

::: {.card title="Logistic Summary-Smog Rating"}


For our final model, we will use logistic regression to also explore the Smog rating variable.

In this model, we can see that combined fuel consumption and transmission AM are the most important predictors. The coefficients of the equation are given below.

```{r}
#Model and capture metrics
#Define the model specification
log_spec <- logistic_reg() %>%
             set_engine('glm') %>%
             set_mode('classification')



#Fit the model
log_smog_fit1 <- logistic_spec %>%
              fit(smog_rating ~ .-cylinders-CO2_rating_Low, data = df_smog_norm_train)

#Capture the predictions and metrics

pred_smog_log_fit1 <- augment(log_smog_fit1, df_smog_norm_test)

```

```{r}
tidy(log_smog_fit1$fit) %>%
  kable(digits=2)
```

:::

::: {.card title="Pruned Logistic Regression Equation"}
```{r}
#Fit the pruned model and capture new metrics
log_smog_fit2 <- logistic_spec %>%
              fit(smog_rating ~ .-cylinders-CO2_rating_Low-fuel_type_regular_gasoline-fuel_type_premium_gasoline-fuel_type_ethanol-vehicle_class_Two.seater-vehicle_class_Subcompact	-vehicle_class_Others	-vehicle_class_Minicompact-vehicle_class_Mid.size		-vehicle_class_Full.size	-make_Porsche- transmission_AV-vehicle_class_SUV..Small	, data = df_smog_norm_train)

#Capture the predictions and metrics

pred_smog_log_fit2 <- augment(log_smog_fit2, df_smog_norm_test)


#Capture the predictions and metrics
pred_smog_log2_fit <- augment(log_smog_fit2,df_smog_norm_test)

curr_metrics <- pred_smog_log2_fit %>%
  my_class_metrics(truth=smog_rating,estimate=.pred_class)
results_cls2 <- tibble(model = "Pruned Smog Rating Logistic Model",
                  Accuracy = curr_metrics[[1,3]],
                  Sensitivity = curr_metrics[[2,3]],
                  Specificity = curr_metrics[[3,3]],
                  Avg_Sens_Spec = (Sensitivity + Specificity)/2,
                  Precision = curr_metrics[[4,3]])

class_smog_rating_tree1_sens <- curr_metrics %>%
  filter(.metric=='sens') %>%
  pull(.estimate)
```

```{r}
#Logistic Equation
tidy(log_smog_fit2$fit) %>%
  kable(digits=2)
```

:::

::: {.card title="Metrics and VI Plot"}
```{r}
#Metrics
results_cls2 %>%
  kable(digits = 2, align = 'l')

#Confusion Matrix
pred_smog_log2_fit %>%
  conf_mat(truth=smog_rating,estimate=.pred_class)

#VIP Plot
vip(log_smog_fit2)
```

:::

### Checking the Logistic Cutoff
::: {.card title="View the ROC Curve"}

```{r}
#ROC Curve
df_roc_smog_rating <- ROC_graph(pred_smog_log2_fit,"smog_rating",".pred_High","log_Smog_rating")
```

:::

::: {.card title="Best Threshold "}

```{r}
best_smog_cut_log <- ROC_threshold(pred_smog_log2_fit,"smog_rating",".pred_High")
best_smog_cut_log  %>%
  kable(digits=2)

#Adding a new cutoff prediction column
pred_smog_log2_fit <- pred_smog_log2_fit %>%
                    mutate(pred_High_bestcut = factor(ifelse(.pred_High > best_smog_cut_log[[1]],"High","Low"),
                                              levels=c("High","Low")))
                                              
# Confusion matrix for New Logistic Cutoff 
pred_smog_log2_fit %>%
  conf_mat(truth=smog_rating,estimate=pred_High_bestcut)

# Metrics
curr_metrics <- pred_smog_log2_fit %>%
  my_class_metrics(truth=smog_rating,estimate=pred_High_bestcut)
results_new <- tibble(model = paste("Logistic Model Smog Rating Best Cutoff",round(best_smog_cut_log[[1]],2)),
                  Accuracy = curr_metrics[[1,3]],
                  Sensitivity = curr_metrics[[2,3]],
                  Specificity = curr_metrics[[3,3]],
                  Avg_Sens_Spec = (Sensitivity + Specificity)/2,
                  Precision = curr_metrics[[4,3]])
results_cls2 <- bind_rows(results_cls2, results_new)

results_cls2 %>%
  kable(digits = 2, align = 'l')
```
:::

# Conclusion
## Row

::: {.card title="Summary"}

In Conclusion, we can see that our predictors do help to predict the median value, either the high/low median value (with cutoff at $30,000) or the actual median values.

Combining the results of both types of predictor models and only reporting where agreement was found, we can see that as these variables increase they:
```{r}
#final table summary of predictor changes
predchangfnl = tibble(Decrease_CO2_emissions =
                            c("Vehicles manufactured by Toyota",
                             "Vehicles with AV(continuous variation) transmission",
                            "Vehicles using ethanol fuel",
                             "Vehicles using regular gasoline fuel"),
                    Increase_CO2_emissions = c(
                      "engine size of vehicles",
                      "Vehicles manufactured by Ford and Porsche",
                      "Vehicle class such as minicompact, pickup truck, sport utility, SUV & Two seater",
                      ""))
predchangfnl %>%
  kable()
```

:::

## Row

::: {.card title="Predicting Continuous CO2 emissions"}

In addition, if we compare the models that we examined for predicting continuous CO2 emissions, we see that the Tune Random Forest and the Gradient Boosted Tree performed much better than the linear regression and Regression Tree models.

* Final Linear Regression MAE: 21.65
* Regression Tree MAE: 11.65
* Tuned RF Tree MAE: 1.54
* Tuned Gradient Boosted Tree MAE: 1.31

```{r}
#Metrics
results_reg %>%
  kable(digits=2, align = 'l')
```

:::

::: {.card title="Compare actual (CO2_emissions) vs predicted (y_hat) tuned tree"}
```{r}
df_act_pred <- bind_rows(
            pred_reg1_fit %>% mutate(model = 'Linear Model'),
            pred_reg2_fit %>% mutate(model = 'Linear Final Model'),
            pred_tree1_fit %>% mutate(model = 'Tuned Reg Tree Model'),
            pred_final_fuel_rf%>% mutate(model = 'Tuned RF Tree Model'),
            pred_final_fuel_xgb%>% mutate(model = 'Tuned Gradient Boosted Model')
)
ggplotly(ggplot(df_act_pred, aes(y = .pred, x = CO2_emissions, color=model)) +
  geom_point() +
    geom_abline(col = "gold") +
    ggtitle("Predicted vs Actual Median Value") )
```

:::

## Row

::: {.card title="Predicting CO2_rating and Smog Rating Value"}
Predicting Categorical CO2 Rating

Comparing the models we examined for predicting the categorical response CO2 rating, we observed that they are similar but the classification tree has higher precision,accuracy and specificity and  similar sensitivity to the best logistic model.

* Classification Tree (cutoff `r round(best_cut_ct[[1]],2)`) Accuracy .989 Sensitivity .994 Specificity 0.988 Precision .956
* Logistic Regression (cutoff `r round(best_cut_log[[1]],2)`) Accuracy .988 Sensitivity .994 Specificity 0.986 Precision .951

```{r}
#Metrics
results_cls %>%
  kable(digits=2, align = 'l')
```

Predicting Categorical Smog Rating

Looking at the logistic model for Smog rating, we observed that best cutoff this model has a higher sensitivity, accuracy and average sensitivity+ specificity, but the specificity and precision decreased.

* Logistic Regression (cutoff `r round(best_smog_cut_log[[1]],2)`) Accuracy .74 Sensitivity .89 Specificity 0.64 Precision .61


```{r}
#Metrics
results_cls2 %>%
  kable(digits=2, align = 'l')
```

:::

::: {.card title="ROC Curves"}
```{r}
#ROC Curve 
df_roc_CO2_rating <- ROC_graph(pred_log_CO2_final_fit,"CO2_rating",".pred_High","log", df_roc_CO2_rating) 
```
```{r}
#ROC Curve 
df_roc_smog_rating <-ROC_graph(pred_smog_log2_fit,"smog_rating",".pred_High","log")
```


:::

::: {.card title="Reflection"}

Q. What did work hardest on or are you most proud of in your project?

* Formatting the dashboard was something I was worked the hardest on and was proud of in my project. I think it is very important to learn to communicate effectively and formatting this project as a dashboard made us all think about ways to choose and organize information to communicate the results effectively.

Q. What would you do if you had another week to work on the project?

* If I had one more week to work on the project, for the classification models, I would like to try more models for the Smog rating variable. Since the CO2 rating response variable barely had any significant predictors, I tried to see if results for a different categorical response was better. I think it would have been interesting to look at classification trees for Smog Rating or even RF and Boosted Tree models.

:::
